Kung Faux Pandas \\ \large Alternative Facts for Privacy Protection

### 2018-05-31 paper/main.tex
Auto Update from local Sharelatex

\makeatletter

\newenvironment{chapquote}[2][2em]
  {\setlength{\@tempdima}{#1}%
   \def\chapquote@author{#2}%
   \parshape 1 \@tempdima \dimexpr\textwidth-2\@tempdima\relax%
   \itshape}
  {\par\normalfont\hfill--\ \chapquote@author\hspace*{\@tempdima}\par\bigskip}
\makeatother

@@

Perhaps more ominously for researchers, on May 25 , 2018, the European Union's (EU) General Data Protection Regulation (GDPR) has come into full effect \cite{<get the text of the rules cited>}, establishing a new paradigm in data ``ownership'' for that jurisdiction.   In short, this set of rules defines the ``owners'' of data to be people from whom it was collected and obliges anyone possessing  that data to  honor the owners' preferences about how the data is kept and used, including a requirement to deletion of any data at the request of its owner at any time in the future.

@@

Kernel Density Estimator & scipy.stats.gaussian\_kde & KDEPlugin & Useful for inter-related  ordinal and ratio data \\

DataSynthesizer &  <authors> & DataSynthesizerPlugin & Generates a Baysean tree to capture some column relationships \\

\hl{CMF?}  & <authors>  & Can't Remember & Fast \\

>>>>

@@

Perhaps more ominously for researchers, on May 25 , 2018, the European Union's (EU) General Data Protection Regulation (GDPR) has come into full effect \cite{gdpr}, establishing a new paradigm in data ``ownership'' for that jurisdiction.   In short, this set of rules defines the ``owners'' of data to be people from whom it was collected and obliges anyone possessing  that data to  honor the owners' preferences about how the data is kept and used, including a requirement to deletion of any data at the request of its owner at any time in the future.

@@

Kernel Density\\Estimator & scipy.stats.gaussian\_kde & KDEPlugin & Useful for inter-related  ordinal and ratio data \\

DataSynthesizer & Ping et al. & DataSynthesizerPlugin & Generates a Bayesian tree to capture column relationships \\

Synthetic dataset\\Generation Framework & Bindschaedler et al.  & SGFPlugin & Fast \\
